Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-05-02 concurrency/CONCUR 2023/paper.tex
lift William's comment

\wm{The fonts are still off here---for instance, p, n, and n' are mathematical variables, not references to the C code. Fix if we have time.}
We verify the template by proving that \lstinline{traverse} function meets a logically atomic specification, shown in Figure \ref{fig:traverse_lock}.
%\than{Try to avoid using specific name of $\mathrm{tree\_rep}$ for public condition, I suggested to use $\mathrm{Node}$ for generic purpose.}

>>>>

%\wm{The fonts are still off here---for instance, p, n, and n' are mathematical variables, not references to the C code. Fix if we have time.}
We verify the template by proving that \lstinline{traverse} function meets a logically atomic specification, shown in Figure \ref{fig:traverse_lock}.
%\than{Try to avoid using specific name of $\mathrm{tree\_rep}$ for public condition, I suggested to use $\mathrm{Node}$ for generic purpose.}
